% CREATED BY DAVID FRISK, 2016
{CFD Simulation of Fruit Fly Wing Beat Motion}\\
{An investigation of unsteady aerodynamics of fruit-fly wing motion to determine passiveness of different degrees of freedom}\\

{BALA KUMARESH THILEEP KUMAR\\         [0.2cm]
        CHAITHANYA KARRA\\[0.2cm]
        JOHN PAUL PERUMADAN MANNUMMAL\\[0.2cm]
        RAJ GOPALA KRISHNA SUBRAMANI VENKATACHALAM\\[0.2cm]
        SHREEYESH SREENIVASAN}\\
        
Department of Mechanics and Martime Sciences\\
Chalmers University of Technology and University of Gothenburg\setlength{\parskip}{0.5cm}

\thispagestyle{plain}			% Supress header 
\setlength{\parskip}{0pt plus 1.0pt}
\section*{Abstract}
In this report, results from an investigation carried out using CFD on the unsteady aerodynamics of rigid fruit fly wing executing hovering motion is presented. The work was primarily aimed at determining the degree of passiveness of different degrees of freedom involved in the fruit fly wing beat cycle. Adhering to the kinematics obtained from literature, the wing beat cycle was simulated and studied using CFD software. The aerodynamic characteristics calculated from CFD is discussed. The results indicates the active nature of stroke and pitch motions involved in the wing beat motion. The findings from the study also suggests the presence of a partially active elevation motion at the extremes of strokes and this has to be further investigated. A fully coupled CFD simulation can be used to validate findings from this report.

% KEYWORDS (MAXIMUM 10 WORDS)
\vfill
Keywords: Fruit fly, Flapping wing, CFD, Unsteady aerodynamics, Overset mesh, Active and passive motion.

\newpage				% Create empty back of side
\thispagestyle{empty}
\mbox{}